curacao_threeplayers_rest_monster

### 2020-09-30 inst/curacao1962_threeplayers_rest_monster.Rmd
reconfiguration

Then Fisher test:
```{r}
aa <- subset(a,a[,5] != a[,6])
aa <- subset(aa,aa[,3] != "1/2-1/2")

M <- table(aa[,3],white_rested=aa[,5]<aa[,6])
M
fisher.test(M,alternative="greater")
```

@@

```{r,label=hyptest,cache=TRUE}
specificp.gt.test(H,"rest",0)
```

>>>>

Then Fisher test:
```{r}
b <- subset(a,a[,5] != a[,6])
b <- subset(b,abs(b[,5]-b[,6])>1)
b <- subset(b,b[,3] != "1/2-1/2")
b <- cbind(b,white_rested = b[,5] < b[,6])
b

M <- table(b[,3],white_rested=b[,7])
M
fisher.test(M,alternative="greater")
```

@@

```{r,label=hyptestrest,cache=TRUE}
specificp.gt.test(H,"rest",0)
```

```{r,label=hyptestdraw,cache=TRUE}
specificp.gt.test(H,"draw",0)
```

```{r,label=hyptestwhite,cache=TRUE}
specificp.gt.test(H,"white",0)
```
